Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-11-17 paper/sec-optimisation.tex
deleted old plots

>>>>

  \subsection{The role of the overlap between different categories}
\label{sec:overlap}

As has been discussed in Sect.~\ref{sec:analysis}, while the optimization of each
category is performed in an inclusive analysis, after having determined the order
of significance of the separate categories. we turn to a exclusive analysis,
in order that
we can combine consistently the results from the various topologies without double
counting.
%
Here we discuss the role of the overlap
between  different categories, which is of course ignored in the final exclusive
analyses.
%
The idea is to understand how significant the information is on which events satisfy the requirements
of more than one category at the same time.

To illustrate the role of the overlap between the different categories, in
Fig.~\ref{fig:categorisationHisto} we show the fraction of events that satisfy the requirements
of one or more categories, for signal and background events.
%
We consider the following cases:
\begin{itemize}
\item events that satisfy the requirements of one category (resolved,
  intermediate or boosted),
\item events that satisfy the conditions of both the resolved and the intermediate categories,
\item and the same for events that fall both
  into the resolved and boosted categories.
\end{itemize}
 Note that by construction, there is no overlap between the boosted
  and intermediate categories due to the
 orthogonal jet multiplicity cuts.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
%\includegraphics[width=0.65\textwidth]{plots/overlap_categories_C1.pdf}
\caption{\small The fraction of events that satisfy the requirements
  of one or more categories, for signal and background events.
  %
  By construction, there is no overlap between the boosted
  and intermediate categories due to the
   orthogonal jet multiplicity cuts. {\bf update including event weights}
}
\label{fig:categorisationHisto}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

As we can see from Fig.~\ref{fig:categorisationHisto}, an large majority of the events
belong to the resolved category, specially in the background case ($\sim 90\%$) but
also a large part of the signal ($\sim 60\%$).
%
In all the other categories, including
the overlaps, signal events are more likely to belong to them than
background events.
%
In the intermediate category, we have around $\sim$30\% of the signal
events and $\sim$10\% of the background events.
%
For the boosted case, we find $\sim$ 6\% of signal events and
$\sim$2\% of background events.
%
We also find that the overlap between the boosted and the other categories
is small: none with the intermediate (by construction), and then $\sim$3\%
($\sim$0.05\%) of the signal (background) events.
%
The overlap between the resolved and the intermediate is also smaller
than the two categories separately: $\sim$7\%
($\sim$ 3\%) for signal (background) events.

Therefore, from the results of Fig.~\ref{fig:categorisationHisto}
we can conclude that the effect of the overlap between categories would
be small correction with respect to the exclusive selection approach
that we use in this work.
%
Note also that while the majority of signal events are in the resolved
category, since the fraction of background events is also larger,
it is advantageous to use the small fraction of events in the boosted category
since the suppression of the background in this category is larger
than in the others.

### 2015-11-17 paper/sec-results.tex
deleted old plots

In this section we present the results of the 
cut-based analysis and
compare our results with other recent related studies.
%
We study how the signal significance
is modified if only the $4b$ component of the
QCD multi-jet background is taken into account,
but the $2b2j$ and $4j$ components are neglected.
%
We also study the role of the overlap
between the different categories.

@@

  \subsection{The role of the overlap between different categories}
\label{sec:overlap}

As has been discussed in Sect.~\ref{sec:analysis}, while the optimization of each
category is performed in an inclusive analysis, after having determined the order
of significance of the separate categories. we turn to a exclusive analysis,
in order that
we can combine consistently the results from the various topologies without double
counting.
%
Here we discuss the role of the overlap
between  different categories, which is of course ignored in the final exclusive
analyses.
%
The idea is to understand how significant the information is on which events satisfy the requirements
of more than one category at the same time.

To illustrate the role of the overlap between the different categories, in
Fig.~\ref{fig:categorisationHisto} we show the fraction of events that satisfy the requirements
of one or more categories, for signal and background events.
%
We consider the following cases:
\begin{itemize}
\item events that satisfy the requirements of one category (resolved,
  intermediate or boosted),
\item events that satisfy the conditions of both the resolved and the intermediate categories,
\item and the same for events that fall both
  into the resolved and boosted categories.
\end{itemize}
 Note that by construction, there is no overlap between the boosted
  and intermediate categories due to the
 orthogonal jet multiplicity cuts.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.65\textwidth]{plots/overlap_categories_C1.pdf}
\caption{\small The fraction of events that satisfy the requirements
  of one or more categories, for signal and background events.
  %
  By construction, there is no overlap between the boosted
  and intermediate categories due to the
   orthogonal jet multiplicity cuts. {\bf update including event weights}
}
\label{fig:categorisationHisto}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

As we can see from Fig.~\ref{fig:categorisationHisto}, an large majority of the events
belong to the resolved category, specially in the background case ($\sim 90\%$) but
also a large part of the signal ($\sim 60\%$).
%
In all the other categories, including
the overlaps, signal events are more likely to belong to them than
background events.
%
In the intermediate category, we have around $\sim$30\% of the signal
events and $\sim$10\% of the background events.
%
For the boosted case, we find $\sim$ 6\% of signal events and
$\sim$2\% of background events.
%
We also find that the overlap between the boosted and the other categories
is small: none with the intermediate (by construction), and then $\sim$3\%
($\sim$0.05\%) of the signal (background) events.
%
The overlap between the resolved and the intermediate is also smaller
than the two categories separately: $\sim$7\%
($\sim$ 3\%) for signal (background) events.

Therefore, from the results of Fig.~\ref{fig:categorisationHisto}
we can conclude that the effect of the overlap between categories would
be small correction with respect to the exclusive selection approach
that we use in this work.
%
Note also that while the majority of signal events are in the resolved
category, since the fraction of background events is also larger,
it is advantageous to use the small fraction of events in the boosted category
since the suppression of the background in this category is larger
than in the others.

>>>>

In this section we present the results of the 
cut-based analysis and
compare our results with other recent related studies.
%
We study how the signal significance
is modified if only the $4b$ component of the
QCD multi-jet background is taken into account,
but the $2b2j$ and $4j$ components are neglected.
%

@@
